Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2020-06-10 man/figures/schematic_plots.Rmd
figure

limitesX <- c(1925, 2020)

eje_x <- scale_x_continuous(breaks = seq(1925, 2020, by=10), limits=c(1925,2020))
```

@@

pbai <- cro_sites %>% 
  filter(nseries > 5) %>% 
  filter(site == "SJ") %>% 
  ggplot(aes(x=year, y=bai_mean/100, colour=site)) + 
  theme_bw() + ylab('BAI') + xlab("") + 
  geom_ribbon(aes(ymin = (bai_mean - bai_se)/100,
                  ymax = (bai_mean + bai_se)/100,
                  fill=site), alpha=.4, colour=NA) +
  geom_line() + 
  geom_point(size=.8) + 
  scale_colour_manual(values = co) +
  scale_fill_manual(values = co) +
  ylab(expression(paste("BAI (", cm^2, year^-1, ")", sep=''))) +
  theme(panel.grid = element_blank(),
        legend.position = "none", #c(0.2,.8),
        strip.background = element_blank(),
        axis.ticks.length.x.top = unit(-3.5, "pt"),
        axis.title.x.top = element_blank(), 
        axis.text.x.top = element_blank(), 
        panel.border = element_blank(),
        axis.line.y = element_line(), 
        axis.ticks.x = element_blank(), 
        axis.text.x = element_blank()) + 
  eje_x

@@

  p <- ggplot(df, aes_string(x = x, y = y)) +
    geom_errorbar(mapping = yerrorbar, colour = micolor, width = .35, size = .2, 
                  na.rm = TRUE) + 
    geom_bar(stat = 'identity', fill = micolor, colour = micolor) +
    geom_hline(yintercept = 0, colour = 'black', lwd = 0.2) + 
    ylab(my_ylab) +
    # Add line to %GC = 50 
    geom_hline(yintercept = c(50, -50), linetype=2, colour='black', lwd=0.2) +
    theme_bw() +
    theme(panel.grid = element_blank(),
          axis.text.y = element_text(size = 5.5),
          axis.text.x = element_text(size = 6)) +
    coord_cartesian(xlim=limitesX)
    # Customize limits and breaks to min of year data 
  p
}

@@

```{r plot_SJ}
gcsj <- gc_todos %>% dplyr::filter(site == 'gc_sj') %>% 
  plotGC(y = 'gc_md', yse = 'gc_md_se', x = 'year', 
         my_ylab = '% GC', micolor = co, limitesX = limitesX) + 
  xlab('') + xlab('Time') + 
  eje_x + 
  # scale_x_continuous(breaks = xrange, position = 'bottom') + 
  scale_y_continuous(trans = pos_neg_log, 
                     breaks=c(-50, 1, 50)) + 
  geom_hline(yintercept = 1,  lwd=0.2)  +
  theme(
    panel.border = element_blank(),
        axis.line.y = element_line(), 
        axis.ticks.x = element_blank(),
    axis.line.x = element_line(colour = "grey")
  )
```

@@

rwi_sj <- cro_rwi %>% filter(site =="sj") %>% 
  ggplot(aes(x=year, y=res, colour=site)) +
  theme_bw() +
  theme(panel.grid = element_blank(), 
        axis.text = element_text(size=8), 
        legend.position = "none", 
        panel.border = element_blank(),
        axis.line.y = element_line(), 
        axis.ticks.x = element_blank(), 
        axis.text.x = element_blank()) + 
  geom_hline(yintercept = 1, colour = "grey") + 
  geom_line(size=.8) + scale_y_continuous(breaks = seq(0.4,1.8, 0.2)) + 
  ylab("RWI") + xlab("") + 
  geom_vline(xintercept = c(1995, 2005, 2012), linetype = "dotted") + 
  eje_x +
  scale_colour_manual(values = co)

@@

iv_plot <- ivv_mean_year %>% 
  ggplot(aes(x=yr, y=iv_avg)) + 
  geom_line(data=ivv_mean, aes(x=date, y=iv_avg), colour = "gray", alpha=.4) +
  geom_errorbar(aes(ymin = iv_avg - 5*iv_se, ymax = iv_avg + 5*iv_se), width=.3, colour = co_evi) +
  geom_point(size=1, shape=21, fill=co_evi, colour = co_evi) + 
  theme_bw() + ylab("EVI") + xlab("") + 
  theme(panel.grid = element_blank(), 
        panel.border = element_blank(),
        axis.line.y = element_line(), 
        axis.ticks.x = element_blank(), 
        axis.text.x = element_blank()) + 
  scale_x_date(limits = c(as.Date("1920-01-01"), as.Date("2020-12-31")))

@@

sa <- avg_sa_clu %>%
  filter(clu_pop2 =="Northern slope") %>% 
  ggplot(aes(x=yr, y=mean)) + 
  geom_hline(yintercept = 0, size=0.3, colour = "gray") + 
  geom_bar(stat = "identity", fill=co_evi, colour="white", size=.1) + 
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width=.5, colour=co_evi) +
  # facet_wrap(~clu_pop2, nrow = 2) + 
  # scale_fill_manual(values = c("pos" = color_pos, "neg" =  color_neg)) +
  # scale_color_manual(values = c("pos" = color_pos, "neg" =  color_neg)) +
  scale_x_date(limits = c(as.Date("1920-01-01"), as.Date("2020-12-31"))) +  
  ylab('EVI std. Anomaly') + xlab("") +
  theme_bw() +
  theme(panel.grid = element_blank(), 
        panel.border = element_blank(),
        axis.line.y = element_line(), 
        axis.ticks.x = element_blank(), 
        axis.text.x = element_blank())
```

@@

p_spei <- df %>% 
  ggplot(aes(x = date, y = mean)) + 
    geom_bar(stat = "identity", colour="grey", fill="grey") + 
  ylab("SPEI") + xlab("") + 
  theme_bw() +
  theme(panel.grid = element_blank(), 
        panel.border = element_blank(),
        axis.line = element_line()) +
  scale_x_date(limits = c(as.Date("1901-01-01"), as.Date("2016-12-31")), date_labels = "%Y", date_breaks ="5 years")
```

@@

m <- p_spei + iv_plot + sa + a+b+c+plot_layout(ncol = 1)
```

```{r}
saveImage(m, path="./man/figures/svg/", dpi=300, w=25, h=15, fig= "plot_metrics", u = "cm") 
```

>>>>

limitesX <- c(1901, 2016)
limitesD <- c(as.Date("1901-01-01"), as.Date("2016-01-01"))

eje_x <- scale_x_continuous(breaks = seq(1900, 2015, by=5), limits = limitesX)
eje_xdate <- scale_x_date

texto_ejes <- element_text(size = 12) 
titulo_eje_y <- element_text(size=14, face = "bold")

custom_tema <- 
  theme(panel.background = element_blank(), 
        panel.border = element_blank(),
        panel.grid = element_blank(),
        # ejes 
        axis.title.y = element_text(size=14, face = "bold"), 
        axis.text.y = element_text(size = 12),
        # x 
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()
)
```

@@

pbai <- cro_sites %>% 
  filter(nseries > 5) %>% 
  filter(site == "SJ") %>% 
  ggplot(aes(x=year, y=bai_mean/100, colour=site)) + 
  ylab('BAI') + xlab("") + 
  geom_ribbon(aes(ymin = (bai_mean - bai_se)/100,
                  ymax = (bai_mean + bai_se)/100,
                  fill=site), alpha=.4, colour=NA) +
  geom_line() + 
  geom_point(size=.8) + 
  scale_colour_manual(values = co) + 
  scale_y_continuous(breaks = c(10,20), position="right") + 
  scale_fill_manual(values = co) + 
  ylab("BAI") + 
  custom_tema + 
  theme(legend.position = "none", 
        axis.line.y = element_line()) +

  eje_x

@@

  p <- ggplot(df, aes_string(x = x, y = y)) +
    geom_errorbar(mapping = yerrorbar, colour = micolor, width = .35, size = .2, 
                  na.rm = TRUE) + 
    geom_bar(stat = 'identity', fill = micolor, colour = micolor) +
    geom_hline(yintercept = 0, colour = 'black', lwd = 0.2) + 
    ylab(my_ylab) +
    # Add line to %GC = 50 
    geom_hline(yintercept = c(50, -50), linetype=2, colour='black', lwd=0.2) + 
    coord_cartesian(xlim=limitesX)
  p
}

@@

```{r plot_SJ}
gcsj <- gc_todos %>% dplyr::filter(site == 'gc_sj') %>% 
  plotGC(y = 'gc_md', yse = 'gc_md_se', x = 'year', 
         my_ylab = '% GC', micolor = co, limitesX = limitesX) + 
  xlab('') + xlab('Time') + 
  eje_x + 
  # scale_x_continuous(breaks = xrange, position = 'bottom') + 
  scale_y_continuous(trans = pos_neg_log, 
                     breaks=c(-50, 1, 50), position="right") + 
  geom_hline(yintercept = 1,  lwd=0.2) + 
  custom_tema + 
  theme(axis.line.y = element_line(),
        axis.line.x = element_line(colour = "grey"), 
        axis.text.x = element_text())
```

@@

rwi_sj <- cro_rwi %>% filter(site =="sj") %>% 
  ggplot(aes(x=year, y=res, colour=site)) +
  custom_tema + 
  theme(legend.position = "none", 
        axis.line.y = element_line()) +
  geom_hline(yintercept = 1, colour = "grey") + 
  geom_line(size=.8) + scale_y_continuous(breaks = c(0.5, 1, 1.5), position="right") +
                                          # seq(0.4,1.8, 0.2)) + 
  ylab("RWI") + xlab("") + 
  geom_vline(xintercept = c(1995, 2005, 2012), linetype = "dotted") + 
  eje_x +
  scale_colour_manual(values = co)

@@

iv_plot <- ivv_mean_year %>% 
  ggplot(aes(x=yr, y=iv_avg)) + 
  geom_line(data=ivv_mean, aes(x=date, y=iv_avg), colour = "gray", alpha=.4) +
  geom_errorbar(aes(ymin = iv_avg - 5*iv_se, ymax = iv_avg + 5*iv_se), width=.3, colour = co_evi) +
  geom_point(size=1, shape=21, fill=co_evi, colour = co_evi) + 
  ylab("EVI") + xlab("") + custom_tema + 
  theme(axis.line.y = element_line()) + scale_y_continuous(position="right") + 
  scale_x_date(limits = limitesD)

@@

sa <- avg_sa_clu %>%
  filter(clu_pop2 =="Northern slope") %>% 
  ggplot(aes(x=yr, y=mean)) + 
  geom_hline(yintercept = 0, size=0.3, colour = "gray") + 
  geom_bar(stat = "identity", fill=co_evi, colour="white", size=.1) + 
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width=.5, colour=co_evi) +
  # facet_wrap(~clu_pop2, nrow = 2) + 
  # scale_fill_manual(values = c("pos" = color_pos, "neg" =  color_neg)) +
  # scale_color_manual(values = c("pos" = color_pos, "neg" =  color_neg)) +
  scale_x_date(limits = limitesD) + 
  ylab(expression(bold("EVI"["sa"]))) + xlab("") + 
  scale_y_continuous(position="right") +
   custom_tema + 
  theme(axis.line.y = element_line())

@@

p_spei <- df %>% 
  ggplot(aes(x = date, y = mean)) + 
    geom_bar(stat = "identity", colour="grey", fill="grey") + 
  ylab("SPEI") + xlab("") + custom_tema + 
  theme(axis.line = element_line(), 
        axis.text.x = element_text(size=10), 
        axis.ticks.x = element_line()) +
  scale_x_date(limits = limitesD, date_labels = "%Y", date_breaks ="10 years", position = "top")

@@

ev <- iv_plot + theme(plot.margin = unit(c(-5,0,-5,0), "pt"))
evsa <- sa +  theme(plot.margin = unit(c(-5,0,5,0), "pt"))

m <- p_spei + ev + sa + a+b+c+plot_layout(ncol = 1)
```

```{r}
saveImage(m, path="./man/figures/svg/", dpi=300, w=25, h=17, fig= "plot_metrics", u = "cm") 
```
